|

### 2024-08-08 doc/paper.qmd
step 2 finished

Now that it is clear that the number of observations for this project is significantly higher than that in @Leuz_2003 study, in order to illustrate the differences and compare the firm-year observations, Table 1 from @Leuz_2003 was partially replicated (only columns on countries and firm/year observations) to distinguish specific discrepancies that could arise for certain countries. The following representes the (partially) replicated Table 1.

>>>>

Now that it is clear that the number of observations for this project is significantly higher than that in @Leuz_2003 study, in order to illustrate the differences and compare the firm-year observations, Table 1 from @Leuz_2003 was partially replicated (only columns on countries and firm/year observations) to distinguish specific discrepancies that could arise for certain countries.

The results in Table 2 show a higher number of firm-year observations for almost all countries compared to the paper by @Leuz_2003, likely due to database updates leading to a more comprehensive dataset. The trend in the number of firm-year observations across countries is consistent with the paper, with larger capital markets like Japan, the United Kingdom, and the United States having the highest numbers. The distribution of observations in my dataset shows higher mean and median values compared to the paper by @Leuz_2003, indicating a greater overall number of firm-year observations, while the minimum values are relatively close, suggesting that the overall distribution of observations across countries remains broadly similar.

However, there are significant discrepancies, particularly for the United States, which has 41,585 observations compared to 3,792 in the original study, possibly due to more comprehensive data or changes in dataset scope. @Leuz_2003 focuse only on S&P 500 companies for the U.S., while this analysis uses a more comprehensive dataset from the Worldscope database, which includes detailed financial statement data and profile data on public companies globally. This broader scope results in a higher number of firm-year observations for the United States. Despite the differences in absolute numbers, the relative trends across countries align with the paper.
